Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings

### 2016-03-09 manuscript/manuscript_pve.Rmd
new model equation 1

\
(1)
$$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^). Total respiration was calculated as

>>>>

\
(1)
$$P_i = \frac{L~C_\mathrm{day'i}~\sigma_\mathrm{s} - R}{\epsilon_\mathrm{c}}$$

where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^). Total respiration was calculated as
